\documentclass[12pt,fleqn]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\usepackage{hyperref}


\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 160mm
\textheight 200mm
\renewcommand\baselinestretch{1.0}

\pagestyle {plain}
\pagenumbering{arabic}

\newcounter{stepnum}

\title{Group 29 (AKT)\\ Project Approval: Reddit}
\author{
Alex Trudeau\\
	\texttt{400030148}
\and
Kathryn Kodama\\
  	\texttt{400013582}
\and
Tommy Tran\\
	\texttt{001150067}
}

\begin {document}

\maketitle
\pagebreak
\section *{Original Project}
\textbf{Original Project Name:} Reddit Application
\newline  \newline
Reddit is an open source application, the original source code can be viewed on GitHub: \url{https://github.com/reddit/reddit}.  The original project is written in Python, XML, and HTML.
\newline \newline
\textbf{Source Code: }The soure code can be compiled by either opening the Reddit smartphone application (ios and Android) or viewing the website here: \url{https://www.reddit.com/}.  The original code contains 81851 lines of code. 
\newline  \newline
\textbf{Software Purpose: } The purpose of Reddit is a media aggregation / online bulletin board.
\newline  \newline
\textbf{License Information: }  The license of the original project belongs to MIT and allows for public redevelopment.
\newline  \newline
\textbf{Test Cases: }

\begin{itemize}
\item User authentication - login, sign up, and sign out.
\item Creating, deleting, and editing subreddits, threads, and comments.
\item "up-voting" and "down-voting" threads and comments.
\item Sorting threads by most popular and most recent.
\item "Karma points" for posts or comments getting "up-voted".
\end{itemize}

\section *{3XA3 Project}

\textbf{Main Functionality: } Our project will mimic the core functionality of Reddit.  This includes creation of subreddits, threads, and posts.   Users will be able to create an account and login and out.  The application will allow users to up vote and/or down vote posts and will provide the option to sort posts by popularity and most recent.  The "homepage" of our application will aggregate popular posts from each subreddit.  
 \newline  \newline
\textbf{Software Scope and Programming Language: }  The domain knowledge of this project can be completed within one term (October to November 2017).  We will be using JavaScript (TypeScript) as our programming language.  To aid our development we will be using Angular, Ionic 2, MongoDB, Express, and Node.js.  All members have general knowledge of JavaScript, HTML and CSS.  Alex Trudeau specifically has advanced knowledge and experience with Angular 4 and Ionic 2.
 \newline  \newline
\textbf{Specialized Hardware and Software Licensing}:  We plan to create a web application that can also be converted to an android and ios mobile application.  As a result we require an android mobile phone and iphone as additional hardware, which members of our group already own.  No additional Software Licensing is necessary to develop this application.



\end {document}