\documentclass[12pt,fleqn]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{vhistory}


\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 160mm
\textheight 200mm
\renewcommand\baselinestretch{1.0}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\fancyhead[L]{September 25, 2017}
\fancyhead[C]{SE 3XA3: Development Plan}
\fancyhead[R]{AKT}
\pagestyle{fancy}

\pagenumbering{arabic}

\newcounter{stepnum}

\title{Group 29 (AKT)\\ Software Development Plan}
\author{
Alex Trudeau\\
	\texttt{400030148}
\and
Kathryn Kodama\\
  	\texttt{400013582}
\and
Tommy Tran\\
	\texttt{001150067}
}
\date{\today\\Version 1.0}
\begin{document}

\maketitle



\pagebreak
\tableofcontents

\section {Revision History}
\begin{tabular}{ |c| c| c| }
\hline
Version & Date & Comments \\
\hline
1.0 & 25/09/17 & Created document \\
\hline

\end{tabular}


\pagebreak

\section{Team Meeting Plan}
\textbf{Where, When, Frequency, Roles, Rules for Agenda}

\subsection{Meeting Frequency and Details}

Team AKT will meet regularly twice a week with all members present for the duration of the project.  The meetings will take place in Lab (L03) at 8:30am on Wednesdays and 2:30pm on Fridays.  Depending on the progress of the project, a third meeting may be required and will take place at Thode Library on the McMaster University campus; times may vary.  Additional meetings may not require all members to be present.

\subsection{Meeting Roles}
Roles for the each team meeting will be assigned as follows:\\ \\
\textbf{Chair:} The chair of each meeting will be selected on a regular rotating basis.  The chair will be responsible for preparing the meeting agenda (see section 2.3 below).\\ \\
\textbf{Notetaker:} The primary notetaker will be Kathryn Kodama.  If the primary notetaker is not present, either Alex Trudeau or Tommy Tran will fill the role.  The notetaker is responsible for taking meeting minutes when appropriate, that is if there is a large amount of content covered in the meeting or an import design decision has been made.  

\subsection{Meeting Agenda}
As stated in section 2.2 above, each meeting will have a chair who will prepare the meeting agenda.  The notetaker will take meeting minutes when appropriate.  \\ 
Basic Meeting Agenda Outline: \\ \\
\textbf{To be filled out prior to meeting:}
Chair:
Topic Selection: What checkmarks are specified in the documentation that should be completed since the last meeting? 
\\ \\
\textbf{To be completed throughout meeting:}
1. Review Agenda
2. 
\\ \\
\textbf{To be completed at the end of each meeting:}
Written statement on decisions made in meeting.
Reminder of what is to be completed by the next meeting.

\section {Team Communication Plan}
Team AKT will primarily communicate through a Facebook Messenger Chat, Git issues, and in person.  Facebook Messenger will be used for casual conversation such as questions, quick updates, and choosing a meeting time and place if an additional meeting outside of lab hours is required. Git issues will be used for flaws in the code discovered through creation or testing.

\section {Team Member Roles}
\begin{tabular}{ | c | c | }
\hline 
\textbf{Team Member} & \textbf{Roles} \\
\hline
Alex Trudeau & Software Developer, Databasing, User Authentication \\
\hline 
Kathryn Kodama & Software Developer, Documentation \\
\hline
Tommy Tran & Software Developer, Testing \\
\hline

\end{tabular}

\section {Git Workflow Plan}
\section {Proof of Concept Demonstration Plan}
\section {Technology}
\section {Coding Style}
\section {Project Schedule}
\section {Project Review (for Revisions 1)}





\end{document}
